Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-14 draft.tex
tiny tweaks

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^\bu \otimes \fg) \to \cliels(\Omega_c^\bu \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^\bu \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.

@@

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^\bu(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}

\owen{Some easy but important situations to examine:}
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

@@

@@

\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure what the theorem is called when $1-n$ is odd.}

>>>>

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^\bu \otimes \fg) \to \cliels(\Omega_c^\bu \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega^\bu \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^\bu \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.

@@

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^\bu(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}
%
%\owen{Some easy but important situations to examine:}
%\begin{itemize}
%\item When $n=0$, we see naive endomorphisms arise.
%\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
%\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
%\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
%\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
%\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
%\end{itemize}

@@

\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure if or what the theorem is when $1-n$ is odd.}

@@
